Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-10-21 manuscript.tex
20161021

&\vert Sine(x)+\Delta h\vert\le\vert x+arcsin(\Delta h)\vert\\
&sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)), \forall x, \vert\Delta h\vert<1.

@@

in which, the characteristics of the signum above can be obtained by \textcolor{red}{checking} if the sign of $y=(x_1+x_2)(Sine(x_1)+Sine(x_2))$ is alwasys nonnegative.

@@

@@

\begin{mylem}\label{lemma:2}

@@

$\gamma$ is a positive scalar, such that the deployment dynamics can be regulated as desired. $\varphi$ is the boundedness of the lumped uncertainty.

>>>>

&\vert Sine(x)+\Delta h\vert\le\vert x+arcsin(\Delta h)\vert\label{eq:lem11}\\
&sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)), \forall x, \vert\Delta h\vert<1\label{eq:lem12}.

@@

@@

For relation~(\ref{eq:lem11}), let $y=Sine(x)+\Delta h-x-arcsin(\Delta h)$, and we can get its derivative
y' = -1,&x\ge\pi/2,x\le-\pi/2\\
y' = \cos x - 1,&\vert x\vert<\pi/2,
where $y'<0$ means $y$ is a monotone decreasing function. As $x=-arcsin(\Delta h)$, $y=0$, according to the definition of $Sine(x)$, we proceed to get
$$\left.
\begin{aligned}
x\ge-arcsin(\Delta h), y\le0&\Rightarrow 0\le Sine(x)+\Delta h\le x+arcsin(\Delta h)\\
x<-arcsin(\Delta h), y>0&\Rightarrow 0> Sine(x)+\Delta h>x+arcsin(\Delta h)\end{aligned}\right\}\\\\
\Rightarrow\vert Sine(x)+\Delta h\vert\le\vert x+arcsin(\Delta h)\vert.
$$
For Eq.~(\ref{eq:lem12}), considering the case $Sine(x)+\Delta h>0$, when $\vert x\vert<\pi/2$, $Sine(x)+\Delta h>0$ becomes
sin(x)+\Delta h>0&\Rightarrow x>-arcsin(\Delta h)\\
&\Rightarrow x+arcsin(\Delta h)>0,
since $y=arcsin(x)$ is a monotone increasing function. We only need to consider $x\ge\pi/2$ instead of $\vert x\vert\ge\pi/2$ for $x\le-\pi/2$ is meaningless in the case $Sine(x)+\Delta h>0$. It is obvious that $x+arcsin(\Delta h)>0$ due to $\vert arcsin(\Delta h)\vert<\pi/2$. Therefore, we can get
sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)),Sine(x)+\Delta h>0,
and similarly the following equation is reasonable:
sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)),Sine(x)+\Delta h\le0.

@@

\begin{mylem}\cite{Hu2008552}\label{lemma:2}

@@

\textcolor{red}{$\varphi$ is the boundedness of the lumped uncertainty. $\gamma$ is a small or  time-varying positive scalar, $\varphi>1$ and $K_d$ is the designer parameter, such that the deployment dynamics can be regulated as desired.}
